---
title: "Tips for Making Your Poster and GFM Page"
format: revealjs
editor: visual
---

## What is a GitHub-Flavored Markdown Page (GFM)

-   It is the page that you will see when you go to github.com/umdfiresa2024/research-*Team-Name*

-   You can create this page by editing README.qmd in your team's GitHub repository

-   After you Render, a README.md page is created

-   After you commit and push, README.md will be your team's GitHub repository homepage. This is also called your team's GFM page.What is a GitHub-Flavored Markdown Page (GFM)

## Today's Agenda

-   Discuss products required in your team's GFM page and poster

    -   Showcasing work in other programming languages

    -   Formatting the GFM page

    -   Visualizing correlations with a line graph

    -   Formatting regression results

## Showcasing work in other programming languages

Insert -\> Executable Cell -\> Python

## Formatting the GFM page

At the beginning of each chunk, you can enter an option to suppress warnings, messages, and the running of codes

<https://quarto.org/docs/computations/execution-options.html>

**#\| eval: FALSE** if you do not want the code to run when you click Render

**#\| warning: FALSE** if you do not want warning messages to be displayed when you Render

## Visualizing Correlations with a Line Graph {.smaller}

```{r}
#| warning: false
#| message: false
#| echo: true

library("tidyverse")

df<-read.csv("panel.csv")

cities<-c("Charlotte, NC", "Winston-Salem, NC")

df2<-df %>%
  filter(Address %in% cities)

ggplot(data=df2, aes(x=Rainf_tavg, y=pm25, col=Address)) + 
  geom_point() +
  scale_colour_manual(values = c("cornflowerblue", "coral"))+
  theme_bw() 
  

```

[List](https://sape.inf.usi.ch/quick-reference/ggplot2/colour) of colors names in R

## Visualizing Correlations with a Line Graph

```{r}
#| warning: false
#| message: false
#| echo: true

ggplot(data=df2, aes(x=Rainf_tavg, y=pm25, col=Address)) + 
  geom_point() +
  scale_colour_manual(values = c("cornflowerblue", "coral"))+
  geom_smooth(se=FALSE)+
  theme_bw() 
```

## Visualizing Correlations with a Line Graph

Saving the graph as a .png file

```{r}
#| warning: false
#| message: false
#| echo: true

png("bestfit.png", width=6, height=4, units="in", res=500)

ggplot(data=df2, aes(x=Rainf_tavg, y=pm25, col=Address)) + 
  geom_point() +
  scale_colour_manual(values = c("cornflowerblue", "coral"))+
  geom_smooth(se=FALSE)+
  theme_bw() 

dev.off()
```

## Formatting Regression Results

Model 1

```{r}
#| warning: false
#| message: false
#| echo: true

df3<-df2 %>%
  mutate(trt=ifelse(Address=="Charlotte, NC", 1, 0)) %>%
  mutate(trt_time=ifelse(year>2007,1,0))

model1<-lm(pm25 ~ trt*trt_time, data=df3)

summary(model1)
```

## Formatting Regression Results

```{r}
#| warning: false
#| message: false
#| echo: true

library("broom")
library("kableExtra")

#format table
t1<-tidy(model1)[, c(1,2,5)]

#display table
kable(t1, digits=2)
```

## That's it!

-   Slides can be found on ELMs -\> Modules -\> Week 11

-   Don't forget to come in for a Lab Consultation and a Lab Check-in!
