---
title: "What is the Impact of the NOx Budget Program on Each County's NOx Emissions?"
format: gfm
editor: visual
---

Step 1. Install necessary packages.

```{r}
#install.packages("tidyverse")
#install.packages("kableExtra")
```

Step 2. Declare that you will use these packages in this session.

```{r}
library("tidyverse")
library("kableExtra")
```

Step 3. Upload the dataframe that you have created in Spring 2024 into the repository.

Step 4. Open the dataframe into the RStudio Environment.

```{r}
df<-read.csv("data.csv")
```

Step 5. Use the **head** and **kable** function showcase the first 10 rows of the dataframe to the reader.

```{r}
kable(head(df))
```

## Question 1: What is the frequency of this data frame?

Answer: Seasonally, for each year

## Question 2: What is the cross-sectional (geographical) unit of this data frame?

Answer: County (represented by the fips variable)

Step 6. Use the **names** function to display all the variables (column) in the dataframe.

```{r}
names(df)
```

## Question 3: Which column represents the treatment variable of interest?

The treatment variable is a product of two variables: nbp and post.

nbp is equal to 1 if a state is ever regulated by the NOx Budget Program.

post is equal to 0.5 in the year 2003 and equal to 1 in the years 2004 through 2007. Otherwise, post is equal to 0.

smm is equal to 1 in the summer and 0 otherwise.

```{r}
df2<-df %>%
  mutate(post=0) %>%
  mutate(post=ifelse(year>=2004, 1, post)) %>%
  mutate(post=ifelse(year==2003,0.5, post)) %>%
  mutate(nbpxpostxsmm=nbp*post*smm)
```

Answer: nbpxpost

## Question 4: Which column represents the outcome variable of interest?

Answer: nox_emit

Step 7: Create a boxplot to visualize the distribution of the outcome variable under treatment and no treatment.

```{r}
temp<-df2 %>%
  filter(nbp==1)

ggplot(temp, aes(x=nox_emit)) +
  geom_histogram() +
  facet_wrap(~post)
```

Step 8: Fit a regression model $y=\beta_0 + \beta_1 x + \epsilon$ where $y$ is the outcome variable and $x$ is the treatment variable. Use the **summary** function to display the results.

```{r}
model1<-lm(nox_emit ~ nbpxpostxsmm, data=df2)

summary(model1)
```

## Question 5: What is the predicted value of the outcome variable when treatment=0?

Answer: 0.68

## Question 6: What is predicted value of the outcome variable when treatment=1?

Answer: 0.68-0.26 = 0.42

## Question 7: What is the equation that describes the linear regression above? Please include an explanation of the variables and subscripts.

Answer:

$$NOx_{cst} = \beta_0 + \beta_1 (NBP_{c} \times Post_{t} \times Summer_{s}) + \epsilon_{cst}$$

where $NOx_{cst}$ represents NOx emissions (in tons) for each county $c$, season $s$, and year $t$.

NBP represents NBP regulation status.

Post is equal to 1 when the policy is enforced.

Summer is equal to 1 in the summer months.

## Question 8: What fixed effects can be included in the regression? What does each fixed effects control for? Please include a new equation that incorporates the fixed effects.

Answer:

$\mu_{cs}$ is county by season fixed effects to take into account county-level regulation that are in effect in specific seasons.

$\eta_{st}$ is season by year fixed effects to take into account all factors common to a season and a year throughout the United States, such as the development of a new medicine.

$\nu_{state - t}$ is is state by year fixed effects to take into account state-level regulation that are in effect such as the MA State Implementation Plan.

$$NOx_{cst} = \beta_0 + \beta_1 NBP_{cst} + \mu_{cs}+\eta_{st}+\nu_{state-t}+\epsilon_{cst}$$

## Question 9: What is the impact of the treatment effect once fixed effects are included?

Answer:

```{r}
library("fixest")

df3<-df2 %>%
  mutate(cs=fips*smm,
         st=smm*year,
         stXy = paste(state, "-", as.character(year)))

summary(model2<-feols(nox_emit ~ nbpxpostxsmm | cs + st + stXy, data=df3))

```

# Questions for Week 5

## Question 10: In a difference-in-differences (DiD) model, what is the treatment GROUP?

Answer:

## Question 11: In a DiD model, what are the control groups?

Answer:

## Question 12: What is the DiD regression equation that will answer your research question?

## Question 13: Run your DiD regressions below. What are the results of the DiD regression?

## Question 14: What are the next steps of your research?

Step 9: Change the document format to gfm

Step 10: Save this document as README.qmd

Step 11: Render the document. README.md file should be created after this process.

Step 12: Push the document back to GitHub and observe your beautiful document in your repository!

Step 13: If your team has a complete dataframe that includes both the treated and outcome variable, you are done with the assignment. If not, make a research plan in Notion to collect data on the outcome and treatment variable and combine it into one dataframe.
